Comparison of long and short amplicon metabarcoding for determination of fungal species diversity and spatial turnover

### 2019-08-13 writing/MSA2019_presentation.Rnw
database comparisons

>>>>

\begin{frame}{Metabarcoding}
\framesubtitle{rDNA regions}
\includegraphics[width=\linewidth]{rDNA}

\vfill

\tiny
\begin{tabular}{p{0.3\linewidth}p{0.3\linewidth}p{0.3\linewidth}}
SSU & ITS & LSU \\ \midrule
highly conserved w/variable regions & variable (5.8S conserved) & conserved w/variable regions \\[1en] 
used for prokaryotes and all eukaryotes & official barcode for fungi & mostly used for fungi, early phylogenetics \\[1en]
\end{tabular}

\vfill

\begincols
  \begincol{0.3\linewidth}
    \begin{block}{Silva 132}
      2M seqs\\
      700k "Ref NR 99" (clusters)\\
      16k fungi, 60k other eukaryotes, 625k prokaryotes
    \end{block}
  \endcol
  \begincol{0.3\linewidth}
    \begin{block}{Unite 8.0}
      800k seqs \\
      120k "species hypotheses" (clusters)\\
      70k fungi, 40k plants, 10k other euk \\
      some sequences include LSU
    \end{block}
  \endcol
  \begincol{0.3\linewidth}
    \begin{block}{RDP 11 fungal LSU}
      11k seqs\\
      8k fungi, 3k other euk
    \end{block}
  \endcol
\endcols

\end{frame}
